Sample-Based Determination of Angular Observables

### 2014-06-24 draft.tex
started writing the unfolding matrix

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}

%% Shortcuts %%
\newcommand{\dd}{\text{d}}
\newcommand{\refapp}[1]{app.~(\ref{app:#1})}
\newcommand{\refeq}[1]{eq.~(\ref{eq:#1})}
\newcommand{\refsec}[1]{sec.~(\ref{sec:#1})}
\newcommand{\reftab}[1]{tab.~(\ref{tab:#1})}
\newcommand{\nuvec}{\vec{\nu}}
\newcommand{\thvec}{\vec{\vartheta}}
\let\oldtheta\theta
\renewcommand{\theta}{\vartheta}
\newcommand{\GeV}{\text{GeV}}
\newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
\let\eps\varepsilon
\newcommand{\aver}[1]{\langle #1 \rangle}
\newcommand{\what}[1]{\widehat{#1}}
\newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}
\DeclareMathOperator{\cov}{Cov}

@@

\preprint{SI-HEP-2014-xx}
\title{Sample-Based Determination of Angular Observables}
\author{Frederik Beaujean}
\email{frederik.beaujean@lmu.de}
\affiliation{C2PAP, Universe Cluster, Ludwig-Maximilians-Universit\"at M\"unchen, Garching, Germany}
\author{Marcin Chrzaszcz}
\email{marcin.chrzaszcz@uzh.ch}
\author{Nicola Serra}
\email{nicola.serra@cern.ch}
\affiliation{Physik-Institut, Universit\"at Z\"urich, Z\"urich, Switzerland}
\author{Danny van Dyk}
\email{vandyk@tp1.physik.uni-siegen.de}
\affiliation{Theoretische Physik 1, Naturwissenschaftlich-Technische Fakult\"at,
Universit\"at Siegen, Siegen, Germany}

@@

>>>>

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage{hepparticles}
\usepackage{hepnicenames}
\usepackage{hepunits}
%% Shortcuts %%
\newcommand{\dd}{\text{d}}
\newcommand{\refapp}[1]{app.~(\ref{app:#1})}
\newcommand{\refeq}[1]{eq.~(\ref{eq:#1})}
\newcommand{\refsec}[1]{sec.~(\ref{sec:#1})}
\newcommand{\reftab}[1]{tab.~(\ref{tab:#1})}
\newcommand{\nuvec}{\vec{\nu}}
\newcommand{\thvec}{\vec{\vartheta}}
\let\oldtheta\theta
\renewcommand{\theta}{\vartheta}
%\newcommand{\GeV}{\text{GeV}}
\newcommand{\order}[1]{\mathcal{O}\left({#1}\right)}
\let\eps\varepsilon
\newcommand{\aver}[1]{\langle #1 \rangle}
\newcommand{\what}[1]{\widehat{#1}}
\newcommand{\wwhat}[1]{\widehat{\widehat{#1}}}
\DeclareMathOperator{\cov}{Cov}

@@

\preprint{SI-HEP-2014-xx}
\title{Sample-Based Determination of Angular Observables}
\author{Frederik Beaujean}
\email{frederik.beaujean@lmu.de}
\affiliation{C2PAP, Universe Cluster, Ludwig-Maximilians-Universit\"at M\"unchen, Garching, Germany}
\author{Marcin Chrzaszcz}
\email{mchrzasz@cern.ch}
\author{Nicola Serra}
\email{nicola.serra@cern.ch}
\affiliation{Physik-Institut, Universit\"at Z\"urich, Z\"urich, Switzerland}
\author{Danny van Dyk}
\email{vandyk@tp1.physik.uni-siegen.de}
\affiliation{Theoretische Physik 1, Naturwissenschaftlich-Technische Fakult\"at,
Universit\"at Siegen, Siegen, Germany}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%55

\section{Systematic way for determining the acceptance matrix for }

In this section we will give a systematic description on how to obtain unfolding matrix based on MC sample. We start by generating so called flat phase space. In this MC all simulated angular distributions of $\cos \theta_l$, $\cos \theta_k$ and $\phi$ are flat. Assuming the massless limit, and not scalars the PDF has only 9 parameters: $F_l$, and $S_{3,4,5,6s,7,8,9}$:
\begin{multline}
\dfrac{d^4\Gamma}{ \Gamma dq^2 dcos\theta_k dcos\theta_l d\phi}=\dfrac{9}{32\pi}( \dfrac{3}{4} (1-F_l) \sin^2 \theta_k + F_l\cos^2 \theta_k + ( \dfrac{1}{4}(1-Fl)\sin^2 \theta_k \\ -  F_l\cos^2) cos 2\theta_l  + S_3 \sin^2 \theta_k \sin^2 \theta_l \cos2\phi + S_4 \sin2 \theta_k \sin \theta_l \cos\phi +\\ S_5 \sin2 \theta_k \sin \theta_l \cos \phi +  (S_{6s} \sin^2 \theta_k) \cos \theta_l + \\ S_7 \sin 2\theta_k \sin \theta_l \sin \phi +  S_8 \sin 2 \theta_k \sin 2 \theta_l \sin phi + S_9 sin^2 \theta_k \sin^2 \theta_l \sin 2 \phi)
\end{multline}
From theory it is easy to compute that only Fl will have a non zero moment equal to $\dfrac{2}{3}$. Next we apply the detector simulation and selection as done on real data. Then we can measure again all 9 moments which we put in a vector $\overrightarrow{v}$. The first column of an unfolding matrix $M_{unfold}$ will be then equal to $\dfrac{3}{2} \overrightarrow{v}$. Next we can weight selected events accordingly to $f_{s_3}$. From theory one can calculate that only moment corresponding to $S_3$ will be non zero and equal to $\dfrac{32}{225} S3$. Measuring the moments on weighted events and punting them in a vector: $\overrightarrow{v_2}$ leads to second column of unfolding matrix equal the $\dfrac{225}{32} \overrightarrow{v_2}$. Repeating this procedure for all moments will lead to full determination of the unfolding matrix. We provide reader the explicit calculation of the normalization factors for the moments vectors:
\begin{equation}
\dfrac{1}{8\pi} \int_{-1}^{1} d\cos \theta_l \int_{-1}^{1} d\cos \theta_k  \int_{-\pi}^{\pi} d\phi f_{S_{3,4,8,9}}*f_{S_{3,4,8,9}}= \dfrac{32}{225} ,
\end{equation}

\begin{equation}
\dfrac{1}{8\pi} \int_{-1}^{1} d\cos \theta_l \int_{-1}^{1} d\cos \theta_k  \int_{-\pi}^{\pi} d\phi f_{S_{5,6,7}}*f_{S_{5,6,7}}= \dfrac{8}{45} ,
\end{equation}
\begin{equation}
\dfrac{1}{8\pi} \int_{-1}^{1} d\cos \theta_l \int_{-1}^{1} d\cos \theta_k  \int_{-\pi}^{\pi} d\phi f_{F_l}= \dfrac{2}{3} 
\end{equation}
